---
title: "Campaign Track Conditions Showcase"
output: 
  html_document:
    theme: flatly
    toc: false
    code_folding: hide
date: "2025-09-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# Load required libraries
library(tidyverse)
library(DT)
library(knitr)
library(htmltools)
library(bslib)
library(plotly)
library(googledrive)
library(httr)

# Set up the theme
theme <- bs_theme(
  version = 5,
  primary = "#007bff",
  secondary = "#6c757d",
  success = "#28a745",
  info = "#17a2b8",
  warning = "#ffc107",
  danger = "#dc3545",
  light = "#f8f9fa",
  dark = "#343a40"
)
```

```{r debug-data, include=FALSE}
# Internal debugging - not shown in output
# This chunk is now empty - all debugging moved to load-data chunk
```

```{r load-data}
# Load the dataset
data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vSyLbbFkD7PZovG5dcsR77xG9KUX7ZZd6slVMK5-nGa-1MRioNkuIK4LZETy2DFHnhhbYTgi4GtmOUx/pub?gid=1465041612&single=true&output=csv")

# Data loaded successfully
```

```{r debug-data-info, include=FALSE}
# Internal debugging for data - not shown in output
cat("Data loaded successfully\n")
cat("Number of rows:", nrow(data), "\n")
cat("Number of columns:", ncol(data), "\n")
cat("Column names:", paste(names(data), collapse = ", "), "\n")

# Debug: Check the data structure
cat("=== DATA DEBUG INFO ===\n")
cat("Missing values in key columns:\n")
cat("age_group:", sum(is.na(data$age_group)), "out of", nrow(data), "\n")
cat("gender:", sum(is.na(data$gender)), "out of", nrow(data), "\n")
cat("policy_issue:", sum(is.na(data$policy_issue)), "out of", nrow(data), "\n")
cat("ideology_congruency:", sum(is.na(data$ideology_congruency)), "out of", nrow(data), "\n")

# Check unique values
cat("Unique age_groups:", paste(unique(data$age_group), collapse = ", "), "\n")
cat("Unique genders:", paste(unique(data$gender), collapse = ", "), "\n")
cat("Unique policy_issues:", paste(unique(data$policy_issue), collapse = ", "), "\n")
cat("Unique ideology_congruency:", paste(unique(data$ideology_congruency), collapse = ", "), "\n")
cat("========================\n")

# Get unique policy issues
policy_issues <- data %>%
  distinct(policy_issue) %>%
  arrange(policy_issue)

# Get unique conditions grouped by policy issue
conditions_by_issue <- data %>%
  distinct(age_group, gender, policy_issue, ideology_congruency) %>%
  arrange(policy_issue, age_group, gender, ideology_congruency)

# Google Drive folder URL for images
drive_folder_url <- "https://drive.google.com/drive/folders/1iZc512V8SFubLegZ70O__d24FBPtq_bs"

# Google Drive Authentication Setup
options(
  gargle_oauth_cache = "~/.R/gargle",           # where tokens live
  gargle_oauth_email = "favoone4@gmail.com"     # auto-picks this account
)

# Function to get file IDs from Google Drive folder
get_drive_file_ids <- function(folder_id = "1iZc512V8SFubLegZ70O__d24FBPtq_bs") {
  cat("Checking Google Drive authentication...\n")
  if (!googledrive::drive_has_token()) {
    cat("No token found, authenticating...\n")
    googledrive::drive_auth()
  } else {
    cat("Token found, proceeding...\n")
  }
  
  cat("Attempting to list files in folder:", folder_id, "\n")
  tryCatch({
    files <- googledrive::drive_ls(googledrive::as_id(folder_id))
    cat("Successfully retrieved", nrow(files), "files from Google Drive\n")
    setNames(files$id, files$name)
  }, error = function(e) {
    cat("Error accessing Google Drive folder:", e$message, "\n")
    return(c())
  })
}

# Cache file IDs to avoid hitting API each render
id_cache <- ".cache/drive_ids.rds"
dir.create(".cache", showWarnings = FALSE)

# Always refresh Google Drive files to get new images
file_id_mapping <- get_drive_file_ids()
saveRDS(file_id_mapping, id_cache)

# Additional direct image links mapping
# You can use these file IDs directly in your data's image columns
# Example: Set image_1 = "1Fg1NO1wxWs2f0qdKnmJgkERRUNtvEOi2" in your data
direct_image_links <- c(
  "1Fg1NO1wxWs2f0qdKnmJgkERRUNtvEOi2" = "https://drive.google.com/file/d/1Fg1NO1wxWs2f0qdKnmJgkERRUNtvEOi2/view?usp=drive_link",
  "1yXxfTTM7TJ5afXDdwD6fuLjdXXXmxSVr" = "https://drive.google.com/file/d/1yXxfTTM7TJ5afXDdwD6fuLjdXXXmxSVr/view?usp=drive_link",
  "1O2Ps1uzVA_DUqKZIOeqF6-xXoB5sH2Ph" = "https://drive.google.com/file/d/1O2Ps1uzVA_DUqKZIOeqF6-xXoB5sH2Ph/view?usp=drive_link",
  "1OhLCJk3Jpk83SyidpMVmlNfhHQJmHzY7" = "https://drive.google.com/file/d/1OhLCJk3Jpk83SyidpMVmlNfhHQJmHzY7/view?usp=drive_link",
  "1P2Kgo1BOOEnuXh0RINgeIgS-AKPS40gX" = "https://drive.google.com/file/d/1P2Kgo1BOOEnuXh0RINgeIgS-AKPS40gX/view?usp=drive_link",
  "1oJbq2eNA4rUBhMwoM5CPOObCLVfnJ7Fn" = "https://drive.google.com/file/d/1oJbq2eNA4rUBhMwoM5CPOObCLVfnJ7Fn/view?usp=drive_link",
  "1hm0uHVACJGJ3vTjljLtiSHdxXouQcAmT" = "https://drive.google.com/file/d/1hm0uHVACJGJ3vTjljLtiSHdxXouQcAmT/view?usp=drive_link"
)

# Function to check if an image name is a direct file ID
is_direct_file_id <- function(image_name) {
  return(image_name %in% names(direct_image_links))
}

# Test function to verify download works
test_download <- function(file_id) {
  cat("Testing download for file ID:", file_id, "\n")
  
  # Test direct download URL
  test_url <- paste0("https://drive.google.com/uc?export=download&id=", file_id)
  cat("Test URL:", test_url, "\n")
  
  # Try download.file
  test_path <- "test_download.webp"
  tryCatch({
    download.file(test_url, test_path, mode = "wb")
    if(file.exists(test_path)) {
      file_size <- file.size(test_path)
      cat("Download successful! File size:", file_size, "bytes\n")
      if(file_size > 1000) {  # More than 1KB
        cat("File appears to be valid image\n")
        unlink(test_path)  # Clean up
        return(TRUE)
      } else {
        cat("File too small, might be HTML error page\n")
        unlink(test_path)
        return(FALSE)
      }
    } else {
      cat("Download failed - no file created\n")
      return(FALSE)
    }
  }, error = function(e) {
    cat("Download error:", e$message, "\n")
    return(FALSE)
  })
}

# Debug: Print file mapping info (moved to internal chunk)
```

```{r debug-drive, include=FALSE}
# Internal debugging for Google Drive - not shown in output
cat("Number of files found in Google Drive:", length(file_id_mapping), "\n")
if(length(file_id_mapping) > 0) {
  cat("All available file names:\n")
  for(i in seq_along(file_id_mapping)) {
    cat("  ", names(file_id_mapping)[i], "->", file_id_mapping[i], "\n")
  }
}

cat("Direct file IDs available:\n")
for(id in names(direct_image_links)) {
  cat("  ", id, "->", direct_image_links[id], "\n")
}

# Test download with your specific file ID
cat("\n=== TESTING DOWNLOAD ===\n")
test_result <- test_download("1hm0uHVACJGJ3vTjljLtiSHdxXouQcAmT")
cat("Test result:", test_result, "\n")
cat("========================\n")

# Function to download image from Google Drive and return local path
download_image <- function(image_name) {
  if(is.na(image_name) || image_name == "") return("")
  
  # Create local images directory
  local_dir <- "ai_experiment_images"
  if(!dir.exists(local_dir)) {
    dir.create(local_dir, showWarnings = FALSE)
  }
  
  # Check if image already exists locally
  local_path <- file.path(local_dir, image_name)
  if(file.exists(local_path)) {
    return(local_path)
  }
  
  # Check if this is a direct Google Drive link
  if(grepl("^https://drive\\.google\\.com/file/d/", image_name)) {
    # Extract file ID from direct link
    file_id <- gsub("^https://drive\\.google\\.com/file/d/([^/]+)/.*", "\\1", image_name)
    if(file_id != image_name) {
      # Try googledrive package first
      tryCatch({
        googledrive::drive_download(
          googledrive::as_id(file_id),
          path = local_path,
          overwrite = TRUE
        )
        if(file.exists(local_path) && file.size(local_path) > 0) {
          return(local_path)
        }
      }, error = function(e) {
        # Fallback to direct download URL
        tryCatch({
          # Use the correct Google Drive download URL format
          download_url <- paste0("https://drive.google.com/uc?export=download&id=", file_id)
          httr::GET(download_url, httr::write_disk(local_path, overwrite = TRUE))
          if(file.exists(local_path) && file.size(local_path) > 0) {
            return(local_path)
          }
        }, error = function(e2) {
          # Try alternative download method with download.file
          tryCatch({
            download_url <- paste0("https://drive.google.com/uc?export=download&id=", file_id)
            download.file(download_url, local_path, mode = "wb")
            if(file.exists(local_path) && file.size(local_path) > 0) {
              return(local_path)
            }
          }, error = function(e3) {
            return("")
          })
        })
      })
    }
  }
  
  # Try to find the file with fuzzy matching
  file_id <- NULL
  
  # First check if it's a direct file ID from our additional links
  if(is_direct_file_id(image_name)) {
    file_id <- image_name
  } else {
    # Safe exact match lookup from Google Drive folder
    exact_match <- tryCatch({
      file_id_mapping[[image_name]]
    }, error = function(e) {
      NULL
    })
    
    if(!is.null(exact_match) && exact_match != "" && !is.na(exact_match)) {
      file_id <- exact_match
    } else {
    # Try fuzzy matching - look for similar names
    # Remove extra .webp extensions
    clean_name <- gsub("\\.webp\\.webp$", ".webp", image_name)
    if(clean_name != image_name) {
      file_id <- tryCatch({
        file_id_mapping[[clean_name]]
      }, error = function(e) NULL)
    }
    
    # Try without .webp extension
    if(is.null(file_id) || file_id == "" || is.na(file_id)) {
      no_webp <- gsub("\\.webp$", "", image_name)
      file_id <- tryCatch({
        file_id_mapping[[no_webp]]
      }, error = function(e) NULL)
    }
    
    # Try partial matching
    if(is.null(file_id) || file_id == "" || is.na(file_id)) {
      available_names <- names(file_id_mapping)
      # Look for names that contain the key parts
      key_parts <- strsplit(image_name, "_")[[1]]
      for(available_name in available_names) {
        if(all(sapply(key_parts[1:3], function(part) grepl(part, available_name, fixed = TRUE)))) {
          file_id <- tryCatch({
            file_id_mapping[[available_name]]
          }, error = function(e) NULL)
          break
        }
      }
    }
  }
  }
  
  if(is.null(file_id) || file_id == "" || is.na(file_id)) {
    return("")
  }
  
  # Download the image from Google Drive
  tryCatch({
    # Use googledrive to download the file
    googledrive::drive_download(
      googledrive::as_id(file_id),
      path = local_path,
      overwrite = TRUE
    )
    if(file.exists(local_path) && file.size(local_path) > 0) {
      return(local_path)
    }
  }, error = function(e) {
    # Try alternative download method with correct URL format
    tryCatch({
      # Use the correct Google Drive download URL format
      download_url <- paste0("https://drive.google.com/uc?export=download&id=", file_id)
      httr::GET(download_url, httr::write_disk(local_path, overwrite = TRUE))
      if(file.exists(local_path) && file.size(local_path) > 0) {
        return(local_path)
      }
    }, error = function(e2) {
      # Try download.file as final fallback
      tryCatch({
        download_url <- paste0("https://drive.google.com/uc?export=download&id=", file_id)
        download.file(download_url, local_path, mode = "wb")
        if(file.exists(local_path) && file.size(local_path) > 0) {
          return(local_path)
        } else {
          return("")
        }
      }, error = function(e3) {
        return("")
      })
    })
  })
}

# Function to create mock post
create_mock_post <- function(text, image_name, author, time_ago) {
  if(is.na(text) || text == "") text <- ""
  if(is.na(image_name) || image_name == "") image_name <- ""

  # Extract initials for avatar
  author_parts <- strsplit(author, "_")[[1]]
  initials <- paste0(substr(author_parts[1], 1, 1), substr(author_parts[2], 1, 1))

  cat('<div class="mock-post">\n')

  # Post header with avatar
  cat('<div class="post-header">\n')
  cat('<div class="post-avatar">', initials, '</div>\n')
  cat('<div class="post-meta">\n')
  cat('<div class="post-author-row">\n')
  cat('<div class="post-author">', author_parts[1], ' ', author_parts[2], '</div>\n')
  cat('<div class="post-handle">@', author, '</div>\n')
  cat('<div class="post-time">· ', time_ago, '</div>\n')
  cat('</div>\n')
  cat('</div>\n')
  cat('</div>\n')

  # Post text
  if(text != "") {
    cat('<div class="post-text">', text, '</div>\n')
  }

  # Post image
  if(image_name != "") {
    local_image_path <- download_image(image_name)
    cat('<div class="post-image">\n')
    if(local_image_path != "" && !is.na(local_image_path) && file.exists(local_image_path)) {
      # Use local image file
      cat('<img src="', local_image_path, '" alt="', image_name, '">\n')
    } else {
      # Show placeholder with link to Google Drive
      cat('<div style="text-align: center; padding: 40px; background-color: #1a1a1a; border-radius: 16px; border: 2px dashed #2f3336;">\n')
      cat('<div style="font-size: 48px; margin-bottom: 16px;">📷</div>\n')
      cat('<div style="font-size: 14px; color: #71767b; margin-bottom: 8px;">', image_name, '</div>\n')
      cat('<a href="', drive_folder_url, '" target="_blank" style="color: #1d9bf0; text-decoration: none; font-size: 12px;">View in Google Drive</a>\n')
      cat('</div>\n')
    }
    cat('</div>\n')
  }

  # Post footer with engagement
  cat('<div class="post-footer">\n')
  cat('<div class="post-engagement comment">\n')
  cat('<span>💬</span>\n')
  cat('<span>', sample(3:20, 1), '</span>\n')
  cat('</div>\n')
  cat('<div class="post-engagement retweet">\n')
  cat('<span>🔄</span>\n')
  cat('<span>', sample(5:25, 1), '</span>\n')
  cat('</div>\n')
  cat('<div class="post-engagement heart">\n')
  cat('<span>❤️</span>\n')
  cat('<span>', sample(20:100, 1), '</span>\n')
  cat('</div>\n')
  cat('<div class="post-engagement share">\n')
  cat('<span>📤</span>\n')
  cat('</div>\n')
  cat('</div>\n')
  cat('</div>\n')
}
```

<style>
.nav-tabs {
  border-bottom: 2px solid #007bff;
}
.nav-tabs .nav-link {
  border: 1px solid transparent;
  border-top-left-radius: 0.375rem;
  border-top-right-radius: 0.375rem;
  margin-right: 2px;
  background-color: #f8f9fa;
  color: #495057;
}
.nav-tabs .nav-link:hover {
  border-color: #e9ecef #e9ecef #dee2e6;
  background-color: #e9ecef;
}
.nav-tabs .nav-link.active {
  color: #495057;
  background-color: #fff;
  border-color: #007bff #007bff #fff;
  border-bottom: 1px solid #fff;
}
.tab-content {
  padding: 20px;
  border: 1px solid #dee2e6;
  border-top: none;
  background-color: #fff;
}
.condition-card {
  border: 1px solid #ddd;
  border-radius: 8px;
  padding: 20px;
  margin: 10px 0;
  background-color: #f9f9f9;
}
.image-container {
  text-align: center;
  margin: 20px 0;
}
.image-container img {
  max-width: 100%;
  height: auto;
  border-radius: 8px;
  box-shadow: 0 4px 8px rgba(0,0,0,0.1);
  margin: 10px;
}
.text-content {
  background-color: white;
  padding: 15px;
  border-radius: 5px;
  margin: 10px 0;
  border-left: 4px solid #007bff;
}
.condition-header {
  background-color: #007bff;
  color: white;
  padding: 10px;
  border-radius: 5px;
  margin-bottom: 15px;
}
.image-tabs {
  margin-top: 20px;
}
.image-tab-content {
  padding: 15px;
  border: 1px solid #dee2e6;
  border-top: none;
  background-color: #f8f9fa;
}
.mock-post {
  background: linear-gradient(135deg, #000 0%, #0a0a0a 50%, #000 100%);
  color: #fff;
  border-radius: 20px;
  margin: 20px 0;
  overflow: hidden;
  font-family: -apple-system, BlinkMacSystemFont, "Segoe UI", Roboto, Helvetica, Arial, sans-serif;
  max-width: 600px;
  margin-left: auto;
  margin-right: auto;
  border: 1px solid #2f3336;
  position: relative;
  box-shadow: 
    0 4px 20px rgba(0, 0, 0, 0.4),
    0 1px 3px rgba(0, 0, 0, 0.2),
    inset 0 1px 0 rgba(255, 255, 255, 0.05);
  transition: all 0.3s cubic-bezier(0.4, 0, 0.2, 1);
  backdrop-filter: blur(10px);
}
.mock-post::before {
  content: '';
  position: absolute;
  top: 0;
  left: 0;
  right: 0;
  height: 1px;
  background: linear-gradient(90deg, transparent, rgba(29, 155, 240, 0.3), transparent);
  opacity: 0;
  transition: opacity 0.3s ease;
}
.mock-post:hover::before {
  opacity: 1;
}
.mock-post:hover {
  transform: translateY(-4px) scale(1.01);
  box-shadow: 
    0 12px 40px rgba(0, 0, 0, 0.6),
    0 4px 12px rgba(29, 155, 240, 0.1),
    inset 0 1px 0 rgba(255, 255, 255, 0.1);
  border-color: rgba(29, 155, 240, 0.3);
}
.post-header {
  padding: 16px 20px 8px 20px;
  display: flex;
  align-items: flex-start;
  gap: 12px;
}
.post-avatar {
  width: 48px;
  height: 48px;
  border-radius: 50%;
  background: linear-gradient(135deg, #1d9bf0, #0d8bd9, #1a8cd8, #0f7bc7);
  display: flex;
  align-items: center;
  justify-content: center;
  color: white;
  font-weight: 700;
  font-size: 18px;
  flex-shrink: 0;
  border: 2px solid rgba(29, 155, 240, 0.3);
  box-shadow: 
    0 4px 12px rgba(29, 155, 240, 0.4),
    0 0 0 0 rgba(29, 155, 240, 0.1),
    inset 0 1px 0 rgba(255, 255, 255, 0.2);
  transition: all 0.3s cubic-bezier(0.4, 0, 0.2, 1);
  position: relative;
  overflow: hidden;
}
.post-avatar::before {
  content: '';
  position: absolute;
  top: -50%;
  left: -50%;
  width: 200%;
  height: 200%;
  background: conic-gradient(transparent, rgba(255, 255, 255, 0.1), transparent);
  animation: rotate 3s linear infinite;
  opacity: 0;
  transition: opacity 0.3s ease;
}
.post-avatar:hover::before {
  opacity: 1;
}
.post-avatar:hover {
  transform: scale(1.1) rotate(5deg);
  box-shadow: 
    0 8px 20px rgba(29, 155, 240, 0.6),
    0 0 0 4px rgba(29, 155, 240, 0.2),
    inset 0 1px 0 rgba(255, 255, 255, 0.3);
  border-color: rgba(29, 155, 240, 0.6);
}
@keyframes rotate {
  from { transform: rotate(0deg); }
  to { transform: rotate(360deg); }
}
.post-meta {
  flex: 1;
  min-width: 0;
}
.post-author-row {
  display: flex;
  align-items: center;
  gap: 8px;
  margin-bottom: 2px;
}
.post-author {
  font-weight: 700;
  color: #fff;
  font-size: 15px;
  margin: 0;
  white-space: nowrap;
  overflow: hidden;
  text-overflow: ellipsis;
}
.post-handle {
  color: #71767b;
  font-size: 15px;
  margin: 0;
  white-space: nowrap;
}
.post-time {
  color: #71767b;
  font-size: 15px;
  margin: 0;
  white-space: nowrap;
}
.post-text {
  padding: 0 20px 12px 20px;
  font-size: 15px;
  line-height: 1.6;
  color: #fff;
  margin: 0;
  word-wrap: break-word;
  white-space: pre-wrap;
  font-weight: 400;
  letter-spacing: 0.01em;
  position: relative;
  background: linear-gradient(135deg, #fff 0%, #e8f4fd 100%);
  background-clip: text;
  -webkit-background-clip: text;
  -webkit-text-fill-color: transparent;
  animation: textShimmer 3s ease-in-out infinite;
}
.post-text a {
  color: #1d9bf0;
  text-decoration: none;
  position: relative;
  transition: all 0.3s ease;
}
.post-text a::after {
  content: '';
  position: absolute;
  bottom: -2px;
  left: 0;
  width: 0;
  height: 2px;
  background: linear-gradient(90deg, #1d9bf0, #0d8bd9);
  transition: width 0.3s ease;
}
.post-text a:hover::after {
  width: 100%;
}
.post-text a:hover {
  text-shadow: 0 0 8px rgba(29, 155, 240, 0.5);
}
@keyframes textShimmer {
  0%, 100% { 
    background-position: 0% 50%; 
  }
  50% { 
    background-position: 100% 50%; 
  }
}
.post-image {
  margin: 12px 20px 0 20px;
  border-radius: 20px;
  overflow: hidden;
  background: linear-gradient(135deg, #1a1a1a 0%, #0f0f0f 100%);
  border: 1px solid rgba(47, 51, 54, 0.5);
  position: relative;
  box-shadow: 
    0 8px 32px rgba(0, 0, 0, 0.4),
    0 2px 8px rgba(0, 0, 0, 0.2),
    inset 0 1px 0 rgba(255, 255, 255, 0.05);
  transition: all 0.4s cubic-bezier(0.4, 0, 0.2, 1);
}
.post-image::before {
  content: '';
  position: absolute;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  background: linear-gradient(45deg, transparent 30%, rgba(29, 155, 240, 0.1) 50%, transparent 70%);
  opacity: 0;
  transition: opacity 0.3s ease;
  z-index: 1;
}
.post-image:hover::before {
  opacity: 1;
}
.post-image:hover {
  transform: scale(1.03) translateY(-2px);
  box-shadow: 
    0 16px 48px rgba(0, 0, 0, 0.6),
    0 4px 16px rgba(29, 155, 240, 0.2),
    inset 0 1px 0 rgba(255, 255, 255, 0.1);
  border-color: rgba(29, 155, 240, 0.3);
}
.post-image img {
  width: 100%;
  height: auto;
  display: block;
  object-fit: contain;
  max-height: 350px;
  background: linear-gradient(135deg, #1a1a1a 0%, #0f0f0f 100%);
  transition: all 0.3s ease;
  position: relative;
  z-index: 0;
}
.post-image:hover img {
  filter: brightness(1.1) contrast(1.05);
}
.post-footer {
  padding: 12px 20px 16px 20px;
  display: flex;
  justify-content: space-between;
  align-items: center;
  border-top: 1px solid #2f3336;
  margin-top: 12px;
}
.post-engagement {
  display: flex;
  align-items: center;
  gap: 8px;
  cursor: pointer;
  padding: 10px 14px;
  border-radius: 24px;
  transition: all 0.3s cubic-bezier(0.4, 0, 0.2, 1);
  font-size: 13px;
  color: #71767b;
  min-width: 0;
  position: relative;
  overflow: hidden;
  background: linear-gradient(135deg, transparent 0%, rgba(255, 255, 255, 0.02) 100%);
  border: 1px solid transparent;
}
.post-engagement::before {
  content: '';
  position: absolute;
  top: 0;
  left: -100%;
  width: 100%;
  height: 100%;
  background: linear-gradient(90deg, transparent, rgba(255, 255, 255, 0.15), transparent);
  transition: left 0.6s ease;
}
.post-engagement::after {
  content: '';
  position: absolute;
  top: 50%;
  left: 50%;
  width: 0;
  height: 0;
  background: radial-gradient(circle, rgba(29, 155, 240, 0.3) 0%, transparent 70%);
  border-radius: 50%;
  transform: translate(-50%, -50%);
  transition: all 0.3s ease;
}
.post-engagement:hover::before {
  left: 100%;
}
.post-engagement:hover::after {
  width: 100px;
  height: 100px;
}
.post-engagement:hover {
  background: linear-gradient(135deg, rgba(29, 155, 240, 0.1) 0%, rgba(29, 155, 240, 0.05) 100%);
  color: #1d9bf0;
  transform: translateY(-2px) scale(1.05);
  border-color: rgba(29, 155, 240, 0.2);
  box-shadow: 
    0 4px 16px rgba(29, 155, 240, 0.2),
    0 2px 8px rgba(0, 0, 0, 0.1);
}
.post-engagement span:first-child {
  font-size: 18px;
  line-height: 1;
  transition: all 0.3s cubic-bezier(0.4, 0, 0.2, 1);
  position: relative;
  z-index: 2;
}
.post-engagement:hover span:first-child {
  transform: scale(1.2) rotate(5deg);
  filter: drop-shadow(0 0 4px rgba(29, 155, 240, 0.5));
}
.post-engagement span:last-child {
  font-size: 13px;
  font-weight: 500;
  margin-left: 2px;
  position: relative;
  z-index: 2;
  transition: all 0.3s ease;
}
.post-engagement:hover span:last-child {
  transform: scale(1.1);
}
.post-engagement:last-child {
  margin-left: auto;
}
.post-engagement.heart:hover {
  background: linear-gradient(135deg, rgba(249, 24, 128, 0.15) 0%, rgba(249, 24, 128, 0.05) 100%);
  color: #f91880;
  border-color: rgba(249, 24, 128, 0.3);
  box-shadow: 
    0 4px 16px rgba(249, 24, 128, 0.3),
    0 2px 8px rgba(0, 0, 0, 0.1);
}
.post-engagement.retweet:hover {
  background: linear-gradient(135deg, rgba(0, 186, 124, 0.15) 0%, rgba(0, 186, 124, 0.05) 100%);
  color: #00ba7c;
  border-color: rgba(0, 186, 124, 0.3);
  box-shadow: 
    0 4px 16px rgba(0, 186, 124, 0.3),
    0 2px 8px rgba(0, 0, 0, 0.1);
}
.post-engagement.comment:hover {
  background: linear-gradient(135deg, rgba(29, 155, 240, 0.15) 0%, rgba(29, 155, 240, 0.05) 100%);
  color: #1d9bf0;
  border-color: rgba(29, 155, 240, 0.3);
  box-shadow: 
    0 4px 16px rgba(29, 155, 240, 0.3),
    0 2px 8px rgba(0, 0, 0, 0.1);
}
.post-engagement.share:hover {
  background: linear-gradient(135deg, rgba(29, 155, 240, 0.15) 0%, rgba(29, 155, 240, 0.05) 100%);
  color: #1d9bf0;
  border-color: rgba(29, 155, 240, 0.3);
  box-shadow: 
    0 4px 16px rgba(29, 155, 240, 0.3),
    0 2px 8px rgba(0, 0, 0, 0.1);
}

/* Loading Animation for Images */
.post-image.loading {
  position: relative;
}
.post-image.loading::after {
  content: '';
  position: absolute;
  top: 50%;
  left: 50%;
  width: 40px;
  height: 40px;
  margin: -20px 0 0 -20px;
  border: 3px solid rgba(29, 155, 240, 0.3);
  border-top: 3px solid #1d9bf0;
  border-radius: 50%;
  animation: spin 1s linear infinite;
  z-index: 10;
}
@keyframes spin {
  0% { transform: rotate(0deg); }
  100% { transform: rotate(360deg); }
}

/* Floating Particles Effect */
.mock-post::after {
  content: '';
  position: absolute;
  top: 0;
  left: 0;
  right: 0;
  bottom: 0;
  background-image: 
    radial-gradient(circle at 20% 20%, rgba(29, 155, 240, 0.1) 1px, transparent 1px),
    radial-gradient(circle at 80% 80%, rgba(29, 155, 240, 0.05) 1px, transparent 1px),
    radial-gradient(circle at 40% 60%, rgba(29, 155, 240, 0.08) 1px, transparent 1px);
  background-size: 50px 50px, 80px 80px, 60px 60px;
  opacity: 0;
  transition: opacity 0.3s ease;
  pointer-events: none;
  z-index: 1;
}
.mock-post:hover::after {
  opacity: 1;
  animation: float 6s ease-in-out infinite;
}
@keyframes float {
  0%, 100% { transform: translateY(0px); }
  50% { transform: translateY(-10px); }
}

/* Premium Glow Effects */
.mock-post {
  position: relative;
}
.mock-post::before {
  content: '';
  position: absolute;
  top: -2px;
  left: -2px;
  right: -2px;
  bottom: -2px;
  background: linear-gradient(45deg, #1d9bf0, #0d8bd9, #1a8cd8, #0f7bc7);
  border-radius: 22px;
  opacity: 0;
  z-index: -1;
  transition: opacity 0.3s ease;
}
.mock-post:hover::before {
  opacity: 0.3;
  animation: glow 2s ease-in-out infinite alternate;
}
@keyframes glow {
  from { filter: blur(2px); }
  to { filter: blur(4px); }
}

/* Text Selection Styling */
::selection {
  background: rgba(29, 155, 240, 0.3);
  color: #fff;
}
::-moz-selection {
  background: rgba(29, 155, 240, 0.3);
  color: #fff;
}

/* Smooth Scrolling */
html {
  scroll-behavior: smooth;
}

/* Custom Scrollbar */
::-webkit-scrollbar {
  width: 8px;
}
::-webkit-scrollbar-track {
  background: #1a1a1a;
}
::-webkit-scrollbar-thumb {
  background: linear-gradient(135deg, #1d9bf0, #0d8bd9);
  border-radius: 4px;
}
::-webkit-scrollbar-thumb:hover {
  background: linear-gradient(135deg, #0d8bd9, #1d9bf0);
}
</style>


- **Total Conditions**: `r nrow(conditions_by_issue)`
- **Policy Issues**: `r nrow(policy_issues)`
- **Age Groups**: `r paste(unique(conditions_by_issue$age_group), collapse = ", ")`
- **Genders**: `r paste(unique(conditions_by_issue$gender), collapse = ", ")`
- **Ideology Congruency**: `r paste(unique(conditions_by_issue$ideology_congruency), collapse = ", ")`

## Policy Issues

```{r debug-processing, include=FALSE}
# Internal debugging for processing
cat("=== STARTING POLICY TABS CREATION ===\n")
cat("Number of policy issues to process:", nrow(policy_issues), "\n")
cat("Policy issues:", paste(policy_issues$policy_issue, collapse = ", "), "\n")
```

```{r create-policy-tabs, results='asis'}
# Create policy tabs for all issues in the data
# Show all policy issues and all conditions dynamically

for(i in seq_len(nrow(policy_issues))) {
  issue <- policy_issues$policy_issue[i]
  
  # Get conditions for this policy issue
  issue_conditions <- conditions_by_issue %>%
    filter(policy_issue == issue)
  
  cat('### ', issue, ' {.tabset}\n\n')
  
  # Show all conditions for this issue
  max_conditions <- nrow(issue_conditions)
  
  for(j in 1:max_conditions) {
    condition <- issue_conditions[j, ]
    
    # Create tab name
    tab_name <- paste0(condition$age_group, " ", condition$gender, " ", condition$ideology_congruency)
    
    cat('#### ', tab_name, ' {.tabset}\n\n')
    
    # Get the data for this specific condition
    condition_data <- tryCatch({
      data %>%
        filter(age_group == condition$age_group,
               gender == condition$gender,
               policy_issue == condition$policy_issue,
               ideology_congruency == condition$ideology_congruency)
    }, error = function(e) {
      data.frame()  # Return empty data frame
    })
    
    # Check if we found data
    if(nrow(condition_data) == 0) {
      next
    }
    
    # Take the first row
    condition_data <- condition_data[1, ]
    
    # Check if this condition has both text and images (with safe column access)
    has_text_1 <- tryCatch({
      !is.na(condition_data$text_reponse_1[1]) && condition_data$text_reponse_1[1] != ""
    }, error = function(e) FALSE)
    
    has_text_2 <- tryCatch({
      !is.na(condition_data$text_reponse_2[1]) && condition_data$text_reponse_2[1] != ""
    }, error = function(e) FALSE)
    
    has_image_1 <- tryCatch({
      !is.na(condition_data$image_1[1]) && condition_data$image_1[1] != ""
    }, error = function(e) FALSE)
    
    has_image_2 <- tryCatch({
      !is.na(condition_data$image_2[1]) && condition_data$image_2[1] != ""
    }, error = function(e) FALSE)
    
    # Only process if we have at least one complete text+image pair
    if(!((has_text_1 && has_image_1) || (has_text_2 && has_image_2))) {
      next
    }
    
    # Version 1 tab - only show if we have both text and image
    if(has_text_1 && has_image_1) {
      cat('##### Version 1\n\n')
      cat('<div class="mock-posts-container">\n')
      
      author_name <- paste0(condition$age_group, "_", condition$gender, "_", condition$ideology_congruency)
      
      # Safe access to text and image columns
      text_1 <- tryCatch(condition_data$text_reponse_1[1], error = function(e) "")
      image_1 <- tryCatch(condition_data$image_1[1], error = function(e) "")
      
      create_mock_post(text_1, image_1, author_name, "2h")
      
      cat('</div>\n\n')
    }
    
    # Version 2 tab - only show if we have both text and image
    if(has_text_2 && has_image_2) {
      cat('##### Version 2\n\n')
      cat('<div class="mock-posts-container">\n')
      
      author_name <- paste0(condition$age_group, "_", condition$gender, "_", condition$ideology_congruency)
      
      # Safe access to text and image columns
      text_2 <- tryCatch(condition_data$text_reponse_2[1], error = function(e) "")
      image_2 <- tryCatch(condition_data$image_2[1], error = function(e) "")
      
      create_mock_post(text_2, image_2, author_name, "1h")
      
      cat('</div>\n\n')
    }
    
    # Condition details
    cat('##### Condition Details\n\n')
    
    # Safe access to condition detail columns
    outgroup_text <- tryCatch(condition_data$outgroup[1], error = function(e) NA)
    values_text <- tryCatch(condition_data$values[1], error = function(e) NA)
    scenarios_text <- tryCatch(condition_data$scenarios[1], error = function(e) NA)
    slogan_text <- tryCatch(condition_data$slogan[1], error = function(e) NA)
    
    if(!is.na(outgroup_text) && outgroup_text != "") {
      cat('<div class="text-content">\n')
      cat('<h6>Outgroup Description</h6>\n')
      cat('<p>', outgroup_text, '</p>\n')
      cat('</div>\n\n')
    }
    
    if(!is.na(values_text) && values_text != "") {
      cat('<div class="text-content">\n')
      cat('<h6>Values</h6>\n')
      cat('<p>', values_text, '</p>\n')
      cat('</div>\n\n')
    }
    
    if(!is.na(scenarios_text) && scenarios_text != "") {
      cat('<div class="text-content">\n')
      cat('<h6>Scenarios</h6>\n')
      cat('<p>', gsub("•", "•", scenarios_text), '</p>\n')
      cat('</div>\n\n')
    }
    
    if(!is.na(slogan_text) && slogan_text != "") {
      cat('<div class="text-content">\n')
      cat('<h6>Slogan</h6>\n')
      cat('<p><strong>', slogan_text, '</strong></p>\n')
      cat('</div>\n\n')
    }
  }
}
```

## Data Summary

```{r data-summary}
# Create a summary table by policy issue
summary_data <- conditions_by_issue %>%
  group_by(policy_issue, age_group, gender, ideology_congruency) %>%
  summarise(
    n_conditions = n(),
    .groups = 'drop'
  ) %>%
  arrange(policy_issue, age_group, gender, ideology_congruency)

kable(summary_data, 
      caption = "Summary of Conditions by Policy Issue, Demographics and Ideology",
      col.names = c("Policy Issue", "Age Group", "Gender", "Ideology", "Number of Conditions"))

# Create a policy issue summary
policy_summary <- conditions_by_issue %>%
  group_by(policy_issue) %>%
  summarise(
    n_conditions = n(),
    .groups = 'drop'
  ) %>%
  arrange(desc(n_conditions))

kable(policy_summary, 
      caption = "Summary by Policy Issue",
      col.names = c("Policy Issue", "Number of Conditions"))
```

## Notes

- All images are stored in the [Google Drive folder](https://drive.google.com/drive/folders/1iZc512V8SFubLegZ70O__d24FBPtq_bs)
- Each condition has two images and two text responses
- The document is organized by condition ID for easy navigation
- Use the table of contents on the left to jump between conditions
